Hybrid quantum-classical unsupervised data clustering based on the Self-Organizing Feature Map

### 2024-12-12 manuscript/main.tex
Clafiry 'limitation to connectivity'

Another challenge relates to the connectivity limitations of currently available quantum computers. In QASOFM, the ancilla qubit accumulates the distances in the phase information and as such it ideally requires a high connectivity to the $X $ register.  The topology of currently available superconducting quantum processors  presents a significant limitation and consequently to the scaling of the QASOFM algorithm.  A possible solution is to create a large auxiliary network,
but it requires many two-qubit operations, which reduces the accuracy.
Another solution is to use platforms with a star architecture (or all to all connected) which are under development with trapped ion technology \cite{QuantinuumsHSeriesHits}.

>>>>

Another challenge relates to the connectivity limitations of currently available quantum computers. In QASOFM, the ancilla qubit accumulates the distances in the phase information and as such it ideally requires a high connectivity to the $X $ register.  The topology of currently available superconducting quantum processors  presents a significant limitation to connectivity and consequently to the scaling of the QASOFM algorithm.  A possible solution is to create a large auxiliary network,
but it requires many two-qubit operations, which reduces the accuracy.
Another solution is to use platforms with a star architecture (or all to all connected) which are under development with trapped ion technology \cite{QuantinuumsHSeriesHits}.
